R Notebook

### 2019-06-18 microbiome_online.Rmd
updated

ps_merge <- merge_phyloseq(esophagus, atlas1006)

@@

sample_data(batmicrobiome)

@@

@@

@@

@@

@@

```{r}
	setwd("/omega/bashscripts/microbiome")

@@

library(phylogeo)
library("HITChipDB")
library(phangorn)

@@

>>>>

mergedGP = merge_samples(TwinsUK,atlas1006)

ps_merge <- merge_phyloseq(atlas1006, tax_table(TwinsUK))

ps_merge <- merge_phyloseq(TwinsUK, atlas1006)

@@

sample_data(atlas1006)

 sample_data(atlas1006)

 data=subset(pseq.meta, !is.na(mnd))

@@

pseq_temp <- baseline(atlas1006)

temp <- complete.cases(sample_data(atlas1006))

@@

table(sample_data(atlas1006)$nationality)

@@

clostridium <- subset_taxa(pseq, Phylum =="Clostridium cluster I"| "Clostridium cluster XI"|"Clostridium cluster XVI"| "Clostridium cluster III"| "Clostridium cluster XIII"| "Clostridium cluster XVII"| "Clostridium cluster IV"| "Clostridium cluster XVIa"| "Clostridium cluster XVIII" |"Clostridium cluster IX"| "Clostridium cluster XV"| "Uncultured Clostridiales")

@@

  # drops it into different countries
  pseq.subset <- subset_samples(pseq, nationality == "SouthEurope"& gender=="female" )

  clostridium <- subset_samples(pseq, Phylum =="Clostridium")

  library(car)
recode(sample_data(pseq)$nationality, "c('SouthEurope', 'CentralEurope')='A+B'")

  df %>%
   mutate(x= recode(sample_data(pseq)$nationality, "c('SouthEurope', 'CentralEurope')='A+B'"))

sample_data(pseq)$bob[subset_samples(pseq, nationality == "SouthEurope"& nationality == "Scandinavia" )] <- "TEST"

# grabs the nationality from phyloseq
test <- get_variable(pseq,"nationality" ) 
# check you've installed this library
library(forcats)
# this collapses the two varialbes into a new variable AB in this case. The command for multiple changes is fct_collapse(x, AB = c("A","B"), DE = c("D","E"))
test <- fct_collapse(test, AB = c("SouthEurope","CentralEurope"))
# creates a new variable in the phyloseq called mnd
sample_data(pseq)$mnd = test
# checks that it has worked. 
get_variable(pseq,"mnd" )

data$grip6max[data$grprespd==3 & data$sex==1] <- 29.46

# Gives an overview of the data set
sample_data(cdi_schubert)
sample_data(ps_merge)
sample_data(pseq)$nationality

https://www.nature.com/articles/s41467-017-01973-8.pdf?origin=ppub

dietswap

ps_merge <- merge_phyloseq(cdi_schubert, atlas1006)

)

@@

```{r}
	setwd("/omega/bashscripts/microbiomedatarepo/datasets/microbiomeDB")

@@

library(phylogeo)
library("HITChipDB")
library(phangorn)
library(microbiomeutilities)

@@

p <- ggplot(tab) + 
```
